Future challenges for Research Software Engineering

### 2025-05-05 future_challenges_for_RSEng.tex
an idea.

\subsection{Impact of AI and automation}
Is it better than cheap PhDs?

>>>>

\subsection{Impact of AI and automation}
Is it better than cheap PhDs?
FG-NOTE: AI will change the interaction with researchers at a fundamental level. Whereas previously RSEs have been points of knowledge that could translate human language formulated problems into technical descriptions and then provide solutions to it,
I foresee that AI drives this low-key interaction to a highly specialized level of knowledge, since the availability of AI is far better.
